Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-05 manuscript-chicago.Rmd
More removing

@@

Lexical cohesion, then, is a useful indicator of social cohesion in
political crisis. Lexical cohesion happens at the word level. Interlocutor
cohesion happens between speakers. Political cohesion happens at the social
level during moments of political crisis, like civil wars and social movements.
Sociolinguistic cohesion is comprised of lexical, interlocutor, and
socio-political events, where the words and their context reveal the disposition
of socially connected linguistic communities. Sociolinguistic cohesion combines
the elements of lexical cohesion in that it captures the degree of similarity
between what is said, and how it is said. It accounts for the cohesion between
multiple speakers in an environment whose language evolves to become more
aligned and similar. Sociolinguistic cohesion also addresses how groups involved
in political rebellion must have internal cohesion to overcome the collective
action problem to mount sustained resistance to state authority.

@@

At the same time, the foundational theoretical assumptions of a linear world has
been increasingly replaced by ideas from dynamical systems theory. Rather than a
chain of events, time series data can be thought of as nested occurrences, where
mutually constrained parts (e.g., citizens, governments, real-world events,
social media platforms) are constantly interacting, leading to more global
behaviors that are larger than the sum of the parts [@turvey2018lectures].
Linear analyses flatten time series data and ignore the variability that is
fundamental to these systems and their evolution over time. However, when
analyzed as dynamical systems, many phenomena exhibit new nonlinear patterns
that were formerly overlooked. Nonlinear methods provide means for capturing the
rich temporal dynamics and variability that unfold in time series data.

Although a number of other nonlinear methods exist, the primary nonlinear method
used in the current work is cross-recurrence quantification analysis [CRQA;
@zbilut1998detecting] and its offshoot, windowed cross-recurrence quantification
analysis [WCRQA; @webber2005recurrence]. CRQA has successfully been used to gain
a better understanding of many complex human phenomena, including a variety of
human social interactions [for a review, see @fusaroli2014analyzing]. Much as it
has for psychology, we argue that the use of nonlinear methods in the
investigation of political science phenomena will lead to new insights and the
development of more robust theories.

@@

Using cross-recurrence quantification analysis [CRQA; @zbilut1998detecting] and
windowed cross-recurrence quantification analysis [WCRQA;
@webber2005recurrence], we analyzed the co-evolution of social cohesion online
and real-world events. Specifically, using heterogeneous data from March 30,
2012, to June 15, 2012, we compared the social cohesion of Syrian tweets with
the counts of all, positive, and negative real-world events derived from
gold-standard international event data [i.e., the Integrated Crisis Early
Warning System; @DVN/28075_2015].

>>>>

Lexical cohesion, then, is a useful indicator of social cohesion in
political crisis. Lexical cohesion happens at the word level. Interlocutor
cohesion happens between speakers. Political cohesion happens at the social
level during moments of political crisis, like civil wars and social movements.
Sociolinguistic cohesion is comprised of lexical, interlocutor, and
socio-political events, where the words and their context reveal the disposition
of socially connected linguistic communities. It accounts for the cohesion between
multiple speakers in an environment whose language evolves to become more
aligned and similar. Sociolinguistic cohesion also addresses how groups involved
in political rebellion must have internal cohesion to overcome the collective
action problem to mount sustained resistance to state authority.

@@

@@

At the same time, the foundational theoretical assumptions of a linear world has
been increasingly replaced by ideas from dynamical systems theory. Rather than a
chain of events, time series data can be thought of as nested occurrences, where
mutually constrained parts (e.g., citizens, governments, real-world events,
social media platforms) are constantly interacting, leading to more global
behaviors that are larger than the sum of the parts [@turvey2018lectures]. When
analyzed as dynamical systems, many phenomena exhibit new nonlinear patterns
that were formerly overlooked. Nonlinear methods provide means for capturing the
rich temporal dynamics and variability that unfold in time series data.

Although a number of other nonlinear methods exist, the primary nonlinear methods
used in the current work are cross-recurrence quantification analysis [CRQA;
@zbilut1998detecting] and its offshoot, windowed cross-recurrence quantification
analysis [WCRQA; @webber2005recurrence]. CRQA has successfully been used to gain
a better understanding of many complex human phenomena, including a variety of
human social interactions [for a review, see @fusaroli2014analyzing]. Much as it
has for psychology, we argue that the use of nonlinear methods in the
investigation of political science phenomena will lead to new insights and the
development of more robust theories.

@@

Using cross-recurrence quantification analysis [CRQA; @zbilut1998detecting] and
windowed cross-recurrence quantification analysis [WCRQA;
@webber2005recurrence], we analyzed the co-evolution of social cohesion online
and real-world events. Specifically, using heterogeneous data from March 30,
2012, to June 15, 2012, we compared the social cohesion of Syrian tweets with
the counts of all, positive, and negative real-world events derived from
international event data [i.e., the Integrated Crisis Early Warning System;
@DVN/28075_2015].
